Intergroup contact fosters\\more inclusive social identities

### 2018-10-19 manuscript/figures_and_tables.tex
update kfold cv

\begin{table}
\caption{Comparison of models estimating participants' social distance (SD) and feeling thermometer (FT) ratings for each target as a function of group differences and target categorizations. As in Table~\ref{tab:t2}, we selected a more complex model over a simpler model when $\frac{\Delta\textit{ELPD}}{\textit{SE}} \geq 2$. $R^2$ is a Bayesian analogue to $R^2$ in maximum likelihood estimation (Gelman, Goodrich, Gabry, \& Ali, 2017).}
\centering
\figureversion{lining, tabular}
\small	
\begin{tabularx}{\linewidth}{r@{~}rXrrrrrrrr} \toprule
\# &  & Description & $R^2_\text{SD}$ & $R^2_\text{FT}$ & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ & $w$ \\ \midrule 
0 &      & Participant & .23 & .26 & -16964 & 71.0 & - & - & - & .00 \\
1 & vs 0 & Category & .38 & .42 & -16338 & 79.6 & 626.8 & 40.2 & 15.6 & .00 \\
2 & vs 1 & SC/ST    & .38 & .43 & -16317 & 79.6 &  20.1 &  9.8 &  2.1 & .00 \\
3 & vs 2 & OBC      & .39 & .43 & -16293 & 80.5 &  24.2 &  9.7 &  2.5 & .00 \\ \midrule
4 & vs 3 & Categorization & .42 & .47 & -14004 & 120.6 & 217.7 & 22.7 &  9.6 & .00 \\
5 & vs 4 & \ldots~(Category) & .42 & .47 & -13986 & 120.9 &  17.6 &  7.7 &  2.3 & .00 \\
6 & vs 5 & \ldots~(Ingroup) & .42 & .47 & -13988 & 120.8 &  -2.0 &  3.6 & -0.6 & .00 \\
\bottomrule    
\end{tabularx}
\label{tab:t3}
\end{table}

>>>>

\begin{table}
\caption{Comparison of models estimating participants' social distance (SD) and feeling thermometer (FT) ratings for each target as a function of group differences and target categorizations. As in Table~\ref{tab:t2}, we selected a more complex model over a simpler model when $\frac{\Delta\textit{ELPD}}{\textit{SE}} \geq 2$. $R^2$ is a Bayesian analogue to $R^2$ in maximum likelihood estimation (Gelman, Goodrich, Gabry, \& Ali, 2017).}
\centering
\figureversion{lining, tabular}
\small	
\begin{tabularx}{\linewidth}{r@{~}rXrrrrrrrr} \toprule
\# &  & Description & $R^2_\text{SD}$ & $R^2_\text{FT}$ & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ & $w$ \\ \midrule 
0 &      & Participant & .23 & .26 & -16964 & 71.0 & - & - & - & .12 \\
1 & vs 0 & Category & .38 & .42 & -16338 & 79.6 & 626.8 & 40.2 & 15.6 & .02 \\
2 & vs 1 & SC/ST    & .38 & .43 & -16317 & 79.6 &  20.1 &  9.8 &  2.1 & .00 \\
3 & vs 2 & OBC      & .39 & .43 & -16293 & 80.5 &  24.2 &  9.7 &  2.5 & .00 \\ \midrule
4 & vs 3 & Categorization    & .42 & .47 & -16028 & 83.5 & 264.8 & 24.5 & 10.8 & .19 \\
5 & vs 4 & \ldots~(Category) & .42 & .47 & -16007 & 83.6 &  21.1 &  8.7 &  2.4 & .67 \\
6 & vs 5 & \ldots~(Ingroup)  & .42 & .47 & -16025 & 84.3 & -17.4 &  5.9 & -3.0 & .00 \\
\bottomrule    
\end{tabularx}
\label{tab:t3}
\end{table}
